%\title{Overleaf Memo Template}
% Using the texMemo package by Rob Oakes
\documentclass[a4paper,11pt]{texMemo}

\usepackage[parfill]{parskip}
\usepackage{nopageno}

%% Edit the header section here. To include your
%% own logo, upload a file via the files menu.
\memoto{Dr. Scott Schreck}
\memofrom{Jared J.~Thomas}
\memosubject{Manuscript submission to \textit{Wind Energy}}
\memodate{\today}

\begin{document}
	\maketitle
	
	Dear Dr. Schreck,
	
	We have submitted our manuscript "Wake Expansion Continuation: Multi-Modality Reduction in the Wind Farm Layout Optimization Problem" for publication in \textit{Wind Energy}. The manuscript presents a method for allowing gradient-based optimization algorithms to bypass local optima in wind farm layout optimization problems. We refer to our method as wake expansion continuation (WEC). 
	
	The key results presented in the manuscript are summarized as follows:
	\begin{enumerate}
		\item For one case study, we found that the worst optimization results run with WEC were better than the best optimization results run without WEC.
		\item Gradient-based optimizations using WEC required one to two orders of magnitude fewer function calls than our tests with gradient-free optimizations, while finding better results on average.
		\item WEC reduced mean wake loss by one to three percentage points more than gradient-based optimizations run without WEC and by zero to two percentage points more than gradient-free optimizations run with or without WEC.
		\item WEC reduced the standard deviation of wake loss across all case studies compared to gradient-based optimization and for all but one case using gradient-free optimization.
	\end{enumerate}
	
	The novelty of this work lies in applying a Gaussian continuation optimization approach to wind farm layout optimization and in applying Gaussian continuation directly to the existing simulation models rather than creating a surrogate model. While we applied the method to only two wake models, it can be applied to any wake model. 
	
	All authors have approved the submission of this manuscript. The results have not been previously published or submitted for publication in any other journal.

	\bigskip
	
	\bigskip

	Sincerely,
	
	Jared J.~Thomas \\
	jaredthomas@byu.net
	
\end{document}